\begin{center}
     \Large{1. Programming Language Syntax}
\end{center}
\begin{itemize}
    \item A programming Language is a formal framework used to instruct computers to execute a computational process.
    \item The language defines the set of allowed programs, which is separate from the implementation. 
    \item A programming language disregards phonology(sound), morphology(shape) and pragmatics(context), focusing on syntax and semantics.
\end{itemize}

\begin{center}
     \textbf{Syntax and Semantics}
\end{center}
\begin{itemize}
    \item Syntax describes the structure of programs, allowed tokens and how they can be assembled.
    \item Semantics describes the logic and meaning of programs, how they are supposed to execute.
    \item Can be represented by Landin's 4 Levels of Syntax:
\end{itemize}
\begin{center}
    \begin{tabular}{ c c }
    \hline
    Physical & characters, fonts \& Spelling \\
    \rowcolor{yellow}
    Structural & grammar \& token sequence \\
    Abstract & structure of language constructs  \\
    \rowcolor{yellow}
    Core & simplified tree needed to explain language  \\
    \hline
    \end{tabular}
\end{center}
\begin{itemize}
    \item \textbf{Lexer} processes the input into tokens, \textbf{Parser} assembles the tokens into meaningful structures.
    \item Chomsky's Hierarchy of Languages(the larger the type, the more restrictive, equally expressive within tiers):
\end{itemize}
\begin{center}
    \begin{tabular}{ c c }
    \hline
    Type-3 Regular Languages & Regular Expressions,\newline(Non-)Deterministic Finite Automata \(\{a^n|n>= 1\}\) \\
    \rowcolor{yellow}
    Type-2 Context Free Languages & Pushdown Automata, Context Free Grammar \(\{a^nb^n|n>= 1\}\) \\
    Type-1 Context Sensitive Languages & Natural Languages \(\{a^nb^nc^n|n>= 1\}\) \\
    \rowcolor{yellow}
    Type-0 Recursively Enumerable Languages & Turing Machines \\
    \hline
    \end{tabular}
\end{center}
\begin{center}
     \textbf{Macros}
\end{center}
\begin{itemize}
    \item Expanded during preprocessing into code of the programming language, useful for generating custom code.
    \item Needs to worry about recursion(usually not expanded) and scoping issues.
\end{itemize}